### 2015-04-29 README.Rmd
minor fixes

```{r eval=FALSE}
install.packages("taxize")
```

@@

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("taxize", "ropensci")
```

```{r}
library('taxize')
```

@@

```{r}
uids <- get_uid(c("Chironomus riparius", "Chaetopteryx"))
```

@@

```{r}
out <- classification(uids)
lapply(out, head)
```

@@

```{r}
children("Salmo", db = 'ncbi')
```

@@

```{r}
downstream("Apis", db = 'itis', downto = 'Species', verbose = FALSE)
```

@@

```{r}
upstream("Pinus contorta", db = 'itis', upto = 'Genus', verbose=FALSE)
```

@@

```{r}
synonyms("Salmo friderici", db='ubio')
```

@@

```{r}
get_ids(names="Salvelinus fontinalis", db = c('ubio','ncbi'), verbose=FALSE)
```

@@

```{r}
get_ids(names="Poa annua", db = "gbif", rows=1)
```

@@

```{r}
get_ids_(c("Chironomus riparius", "Pinus contorta"), db = 'nbn', rows=1:3)
```

@@

```{r}
sci2comm('Helianthus annuus', db = 'itis')
```

@@

```{r}
comm2sci("black bear", db = "itis")
```

@@

```{r}
as.uid(315567)
```

@@

```{r}
as.uid(list("315567", "3339", "9696"))
```

@@

```{r}
out <- as.uid(c(315567, 3339, 9696))
(res <- data.frame(out))
```

@@

+ [Scott Chamberlain](https://github.com/SChamberlain)
+ [Eduard Szöcs](https://github.com/EDiLD)
+ [Zachary Foster](https://github.com/zachary-foster)
+ [Carl Boettiger](https://github.com/cboettig)
+ [Karthik Ram](https://github.com/karthik)
+ [Ignasi Bartomeus](https://github.com/ibartomeus)
+ [John Baumgartner](https://github.com/johnbaums)

>>>>

```{r install_stable, eval=FALSE}
install.packages("taxize")
```

@@

```{r install_dev, eval=FALSE}
install.packages("devtools")
devtools::install_github("taxize", "ropensci")
```

```{r load}
library('taxize')
```

@@

```{r get_uid}
uids <- get_uid(c("Chironomus riparius", "Chaetopteryx"))
```

@@

```{r classification}
out <- classification(uids)
lapply(out, head)
```

@@

```{r children}
children("Salmo", db = 'ncbi')
```

@@

```{r downstream}
downstream("Apis", db = 'itis', downto = 'Species', verbose = FALSE)
```

@@

```{r upstream}
upstream("Pinus contorta", db = 'itis', upto = 'Genus', verbose=FALSE)
```

@@

```{r synonyms}
synonyms("Salmo friderici", db='ubio')
```

@@

```{r get_ids}
get_ids(names="Salvelinus fontinalis", db = c('ubio','ncbi'), verbose=FALSE)
```

@@

```{r get_ids2}
get_ids(names="Poa annua", db = "gbif", rows=1)
```

@@

```{r get_ids_}
get_ids_(c("Chironomus riparius", "Pinus contorta"), db = 'nbn', rows=1:3)
```

@@

```{r sci2comm}
sci2comm('Helianthus annuus', db = 'itis')
```

@@

```{r comm2sci}
comm2sci("black bear", db = "itis")
```

@@

```{r as.uid}
as.uid(315567)
```

@@

```{r as.uid2}
as.uid(list("315567", "3339", "9696"))
```

@@

```{r as.uid3}
out <- as.uid(c(315567, 3339, 9696))
(res <- data.frame(out))
```

@@

+ [Scott Chamberlain](https://github.com/sckott)
+ [Eduard Szöcs](https://github.com/EDiLD)
+ [Zachary Foster](https://github.com/zachary-foster)
+ [Carl Boettiger](https://github.com/cboettig)
+ [Karthik Ram](https://github.com/karthik)
+ [Ignasi Bartomeus](https://github.com/ibartomeus)
+ [John Baumgartner](https://github.com/johnbaums)
